---
title: "Bioinformatics_Q15"
author: "Hyeonseok Jang (PID A59011126)"
date: "7/16/2022"
output: html_document
---
Load in all the necessary packages for this question.
```{r}
library(ggplot2)
library(lubridate)
library(dplyr)
```

Import data from the CSV file.
```{r}
variants <- read.csv("covid19_variants.csv")
```

See what types of COVID variants are in the data.
```{r}
table(variants$variant_name)
```

Subset the data to remove 'Total' and 'Other' from the 'variant_name' column
```{r}
variants.sequenced <- filter(variants, variant_name!="Total" & variant_name!="Other")
```

Make the 'date' column Date format
```{r}
variants.sequenced$date <- ymd(variants.sequenced$date)
```

Draw a line plot that shows changes in the proportions of each variant over time.
```{r}
variants.trend <- ggplot(data=variants.sequenced,
                         aes(x=date, y=percentage, color=variant_name)) +
                  geom_line(aes(group=variant_name))
variants.trend
```

Modify axis and legend labels, and add a plot title and a caption according to the example figure in the PDF.
```{r}
variants.trend <- variants.trend +
                  labs(x=NULL,
                       y="Percentage of sequenced specimens",
                       color=NULL,
                       title="Covid-19 Variants in California",
                       caption="Data Source: <https://www.cdph.ca.gov/>")
variants.trend
```

Scale x axis and make the theme of plot match that of the example.
```{r}
variants.trend <- variants.trend +
                  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
                  theme_bw() +
                  theme(axis.text.x = element_text(angle = 60, hjust=1))
variants.trend
```